Parameter Space Representation of Pareto Front to Explore Hardware-Software Dependencies

### 2014-10-27 experiments.tex
discussion on sweet spot

The set of default algorithm tuning parameters used for both the
genetic and PS approaches to perform the simulations are shown in
Table~\ref{tab:defaults}. Given the similarity, both in terms of
meaning and functionality, of the parameter $K$ with the population size
of the genetic approach, they both have been set to the same values. As discussed
when introducing the main PS algorithm concepts, an accurate
investigation of algorithm tuning is beyond the scope of this
introductory work. Nevertheless, a set of preliminary tests with
different values of $K$ have been conducted. As shown in
Figure~\ref{fig:kimpact}, which refer to the alloca\_test application
and a fixed amount of 500 configurations, initially increasing values
of $K$ seem to improve both pareto (left picture) and objective
distribution (right picture), but after some threshold the $K$ does
not seem to provide any benefit, even returning to slightly worse
results for the last value considered (100). Similar results have been
reported on average for the different benchmarks considered, which are
not included for space reasons. A complete resource with the whole 
results and data obtained in the tests performed can be found
at~\cite{ps_results}.

>>>>

The set of default algorithm tuning parameters used for both the
genetic and PS approaches to perform the simulations are shown in
Table~\ref{tab:defaults}. Given the similarity, both in terms of
meaning and functionality, of the parameter $K$ with the population size
of the genetic approach, they both have been set to the same values. As discussed
when introducing the main PS algorithm concepts, an accurate
investigation of algorithm tuning is beyond the scope of this
introductory work. Nevertheless, a set of preliminary tests with
different values of $K$ have been conducted. As shown in
Figure~\ref{fig:kimpact}, which refer to the alloca\_test application
and a fixed amount of 500 configurations, initially increasing values
of $K$ seem to improve both pareto (left picture) and objective
distribution (right picture), but after some threshold the $K$ does
not seem to provide any benefit, even returning to slightly worse
results for the last value considered (100). Similar trends have been
found for other benchmarks in the set considered (which are
not included for space reasons), showing a value of $K$ around 30 as
reasonable sweet spot for the objectives. A complete resource with the whole 
results and data obtained in the tests performed can be found
at~\cite{ps_results}.
